Maintenance planning on French military aircraft operations

### 2018-01-09 R/dga_diaporama/dga.Rmd
changed MOSIM article and dga presentation

---
title: "Plannification de maintenances des aéronefs militaires"
author: "Franco Peschiera"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
bibliography: MFMP.bib
nocite: "@*"
output: 
  slidy_presentation: 
    incremental: yes
    css: "./../../css/baobab.css"
---

@@

```{r echo=FALSE}
htmltools::includeHTML("./../../img/calendar.html")
```

@@

<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
</style>

<div class="col2">
```{r echo=FALSE}
htmltools::includeHTML("./../../img/maintenances.html")
htmltools::includeHTML("./../../img/unavailable.html")
```
</div>

>>>>

---
title: "Plannification de maintenances des aéronefs militaires"
author: "Franco Peschiera"
# date: "`r format(Sys.time(), "%Y-%m-%d")`"
output:
  beamer_presentation:
    incremental: yes
  slidy_presentation:
    css: ./../../css/baobab.css
    incremental: yes
nocite: '@*'
bibliography: MFMP.bib
---

@@

![Maintenances](./../../img/calendar.png)
```{r echo=FALSE}
#htmltools::includeHTML("./../../img/calendar.html")
```

@@

<!-- <style> -->
<!--   .col2 { -->
<!--     columns: 2 200px;         /* number of columns and width in pixels*/ -->
<!--     -webkit-columns: 2 200px; /* chrome, safari */ -->
<!--     -moz-columns: 2 200px;    /* firefox */ -->
<!--   } -->
<!-- </style> -->

<!-- <div class="col2"> -->
![Maintenances](./../../img/maintenances.png)

# Exemple (3)
![Affectations](./../../img/unavailable.png)
```{r echo=FALSE}
# htmltools::includeHTML("./../../img/maintenances.html")
# htmltools::includeHTML("./../../img/unavailable.html")
```
<!-- </div> -->

### 2018-01-09 latex/ROADEF2018/article_roadef_2018_alt.tex
changed MOSIM article and dga presentation

\section{Introduction}
    The Military Flight and Maintenance Planning Problem considered here aims to assign missions and maintenance tasks to military aircraft. It is a variant of the Flight and Maintenance Planning problem where flights are not modelled geographically since a round-trip to the base is assumed for each flight. It also includes different objectives and constraints. Although the former has been studied in literature in \cite{Cho2011,Chastellux2017,Kozanidis2008,Verhoeff2015}, it has not received as much attention as the latter. In the following, the problem with already scheduled missions is considered.

@@

\bibliographystyle{plain}
% \selectlanguage{english}
\bibliography{MFMP}

>>>>

\section{Introduction}
    The Military Flight and Maintenance Planning Problem considered here aims to assign missions and maintenance tasks to military aircraft. It is a variant of the Flight and Maintenance Planning problem where flights are not modeled geographically since a round-trip to the base is assumed for each flight. It also includes different objectives and constraints. Although the former has been studied in literature in \cite{Cho2011,Chastellux2017,Kozanidis2008,Verhoeff2015}, it has not received as much attention as the latter. In the following, the problem with already scheduled missions is considered.

@@

\bibliographystyle{plain}
% \selectlanguage{english}
\bibliography{./../biblio/MFMP}
